% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res} 
% the margin option causes section titles to appear to the left of body text 
\textwidth=5.2in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document} 
 
\name{Jiahao Li\\[12pt]} % the \\[12pt] adds a blank line after name
 
\address{{\bf Address} \\ 
         Room 3-2-702 \\
         Shahu Residential Quarter \\
         No. 315 Xudong St. \\
         Wuhan, Hubei, P. R. C. }
\address{{\bf Information} \\ 
         Tel: +86-18607160420 \\ 
         Email: isundaylee@gmail.com \\
         D. O. B.: Apr. 20th 1997 \\}

 
\begin{resume} 

\section{Language Proficiency}
English (fluent, TOEFL score 116), 
Chinese (native)

\section{Programming Languages Skills}
C / C++ (major), 
Objective-C, 
Ruby, 
PHP, 
HTML / CSS, 
Python, 
Pascal, 
Visual Basic, 
Bash Script

\section{Advanced Placement Scores}

\begin{itemize}
    \item{Computer Science AB: 5}
    \item{Calculus BC: 5}
    \item{Physics C Mechanics: 5}
\end{itemize}

\section{Recent Awards}

{\bf General}

\begin{itemize}
    \item{4th Annual Hubei Wenhua Technology Award \hfill Sep. 2011 \\
          Among the 10 (out of 5 million high school students in Hubei province) to receive this award}
    \item{Early acceptance into Peking University \hfill Aug. 2011 \\
          Computer Science major. }
    \item{Early acceptance into Xi'an Jiaotong University \hfill Feb. 2011 \\
          Ranked 1st out of 1260 applicants. }
\end{itemize}

{\bf Olympiad in Informatics}

\begin{itemize}
    \item{17th National Olympiad in Informatics \hfill Nov. 2011 \\
         Provincial, High School Division \\
         Ranked 1st among all contestants of Hubei province. }
    \item{28th National Olympiad in Informatics \hfill Aug. 2011 \\
         National Final, High School Division \\ 
         First Prize, selected into national IOI training camp. }
    \item{Asia-Pacific Informatics Olympiad \hfill May 2011 \\
         China Regional Bronze Prize}
    \item{16th National Olympiad in Informatics \hfill Nov. 2010 \\
         Provicial, High School Division \\
         Ranked 2nd among all contestants of Hubei province. }
\end{itemize}

{\bf Olympiad in Mathematics}

\begin{itemize}
    \item{National Mathematics Competition \hfill Apr. 2010 \\
         Junior School Division \\
         Second Prize}
\end{itemize}

{\bf Olympiad in Physics}

\begin{itemize}
    \item{21st National Practical Physics Competition \hfill Apr. 2011 \\
         First Prize} 
\end{itemize}

\section{Extracurricular Activities}

\begin{itemize}
    \item{
        Created widely received software used by high school teachers in the tests of students' oral English abilities. 
        \begin{itemize}
            \item{About 5000 times being used till December 2011. }
            \item{Currently developing version 2.0. }
        \end{itemize}
        }
    \item{
        Co-founded the Beetle Information Technology Club 
        \begin{itemize}
            \item{Provided students with a platform to know about and get involved in Information Technology by providing C++ programming course. }
            \item{Recognized as the Most Creative Club of the school. I myself recognized as the Most Influential Club Leader. }
        \end{itemize}
        }
    \item{
        Participated in the reception of John Ball GM, US System Builder during his visit to our school. 
        \begin{itemize}
            \item{As the school representative, I was in charge of the reception. I gave an introduction of the history and mission statment of my school, and of the work of the Beetle Information Technology Club to Mr. Ball and his entourage. }
        \end{itemize}
        }
    \item{
        Master of the Graduation Ceremony of Wuhan Foreign Languages School 
        \begin{itemize}
            \item{Hosted the graduation ceremony as the student of honor. }
            \item{Involved in the performance of the student body. }
        \end{itemize}
        }
\end{itemize}

\section{Research Experiences}

\begin{itemize}
    \item{
        Participated in the TuftsTheory research group of the Tufts University. 
        \begin{itemize}
            \item{Mentored by Prof. Diane Souvaine and Ph. D. Candidate Andrew Winslow. }
            \item{Worked on problems about Cellular Automata. }
        \end{itemize}
    }
\end{itemize}

\section{Projects}

\begin{itemize}
    \item{
        Designed and implemented WFLSSU
        \begin{itemize}
            \item{An site for the Student Union of Wuhan Foreign Languages School for managing its membership profiles and other archives. }
            \item{Accessible at {\tt http://wflssu.ljh.me} (In English). }
            \item{Source code available at {\tt http://github.com/isundaylee/wflssu}. Implemented with Ruby on Rails. }
        \end{itemize}
    }
    \item{
        Designed and implemented WFLSer
        \begin{itemize}
            \item{An alumni socialization site for Wuhan Foreign Languages School. }
            \item{Accessible at {\tt http://wflser.org} (In Chinese). }
            \item{Source code available at {\tt http://github.com/isundaylee/alumni}. Implemented with PHP. }
        \end{itemize}
        }
    \item{
        Designed and implemented VIROJ
        \begin{itemize}
            \item{An open-source online code judging system for judging ACM / ICPC style problems. }
            \item{Currently offline. }
            \item{Source code available at {\tt https://code.google.com/p/viroj}. Implemented with PHP. }
        \end{itemize}
    }
\end{itemize}

\section{Publication}

[1] Jiahao Li, ``From Floyd to SPFA'', National Olympiad in Informatics (NOI) Journal, p. 22-23, Dec. 2011. (In Chinese)

\section{Media Exposure}

Featured in several national and local media interviews. 

\begin{itemize}
    \item{Local Newspapers: Changjiang Papers, Wuhan Times, Wuhan Morning Times, Chutian Times, Chutian City Beats and Changjiang Business Report. }
    \item{National Newspapers: NOI Tribune, China Youth Paper, Changjiang Papers, Wuhan Times, Wuhan Morning Times, Chutian Times, Chutian City Beats and Changjiang Business Report. }
    \item{TV: Wuhan Educations Channel, Wuhan 6th Broadcasting Channel and Hubei Television Channel}
\end{itemize}

\end{resume} 
\end{document} 



